\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-09-09 Latex/paper.tex
# convexity adjustment sofr unit test

\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R_{avg}(t_0,t_1)  \right).

@@

F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{P_{ois}(t,t_0)- P_{ois}(t,t_1)}{t_1 - t_0}, \quad t \in [0,t_0] \\

@@

to get the convexity adjustment for $R_{avg}(t_0,t_1)$. Now, if we use (\ref{clark-okone}) and (\ref{malliavin_derive_x}, we have the next representation for $R(t_0,t_1)$ 

@@

&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(\int_{\max(s,t_0)}^{t1} D_s x_u du \right) dW^{\mathbb{Q}}_s \\
&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s\\
&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s

@@

Then, if we use Girsanov's theorem we have that

@@

F(0,t_0,t_1) &\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) \nu(s,t_1)  du ds \\
&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds  

@@

 \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds.

@@

Now, if we use (\ref{log_approximation}) with 
x &= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right)\\
\epsilon &= \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
we can calculate the adjusment for $R_{avg}(t_0,t1)$
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) &\approx \frac{\log\left(1+(t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)\right)}{t_1 - t_0} \\
&-\frac{1}{2(1 + (t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right))^{2}} \int_{0}^{t_1}\left(\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  du\right)^{2} ds

\begin{example}
The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k$ and constant volatility $\sigma$. Then
\end{example}

>>>>

\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).

@@

F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\

@@

to get the convexity adjustment for $R_{avg}(t_0,t_1)$. Now, if we use (\ref{clark-okone}) and (\ref{malliavin_derive_x}), we have the next representation for $R(t_0,t_1)$ 

@@

&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \frac{1}{t_1- t_0} \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(\int_{\max(s,t_0)}^{t1} D_s x_u du \right) dW^{\mathbb{Q}}_s \\
&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s\\
&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) +  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s

@@

Then, if we use Girsanov's theorem and we apply $\mathbb{E}^{\mathbb{Q}^{t_1}}(\cdot)$ we get

@@

F(0,t_0,t_1) &\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \frac{1}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right)  \right) \nu(s,t_1)  du ds \\
&\approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) -  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds  

@@

 \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \frac{1}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  \nu(s,t_1)  du ds.

@@

\begin{example}
The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k$ and constant volatility $\sigma$. It is easy to show in the case of the Hull-White model

\begin{align*}
\eta_s &= \sigma \exp(-ks)\\
\beta(s,u, x_0, \hat{y}_s) &= \sigma \exp(-ku) \\
\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}
\end{align*}
 Therefore, from the last equalities and (\ref{convexity_ois_future}), we have that
\begin{equation}
 \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \frac{\sigma^{2}}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \exp(-ku)   \frac{\exp(-ks) - \exp(-kt_1)}{k} du ds
\end{equation}
\end{example}
Now, in order to compute the convexity adjustmen for the average case, we  wil use (\ref{log_approximation}) with 
\begin{align*}
x &= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right)\\
\epsilon &=  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
\end{align*} 
we can calculate the adjusment for $R_{avg}(t_0,t1)$
\begin{align*}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) &\approx \frac{\log\left(1+(t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)\right)}{t_1 - t_0} \\
&-\frac{1}{2(1 + (t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right))^{2}} \int_{0}^{t_1}\left(\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  du\right)^{2} ds
\end{align*}
